Relationships in the extremes and their influence on competition and coexistence

### 2022-10-10 paper/Paper.Rnw
theory fig with color

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/theory_fig_col.pdf}
\caption{Pedagogical figure to demonstrate how asymmetric tail associations are removed while maintaining original marginal distributions and correlation between variables. (a) the starting variables with ATA. (b) the variables are transformed by a normal inverse cumulative distribution function of their own cumulative distribution function. (with a Spearman correlation of $\rho). Asymmetric association structure is maintained. (c) a newly generated, naturally symmetric, bivariate normal with the correlation, $\ddot{\rho}=\rho. (d) two variables which have the same marginals and correlation as the starting variables in (a) but have a symmetric association structure, obtained by taking the inverse cumulative distribution functions of the starting variables of the normal cumulative distribution function of the normal distributions. For demonstration purposes we start with beta distributed variables, though variables can be distributed differently and the two can be dissimilar. \label{fig:theory}}
\end{figure}
